---
title: "Gapminder"
author: "David Minty"
date: "07/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("gapminder")
library("tidyverse")
```

## Introduction

In this document, we will be exploring the Gapminder dataset.

## Observations of Gapminder

### Countries with life expectancy less than 30

```{r LE<30}
gapminder %>% filter(lifeExp < 30)
```
Life expectancy in **Rwanda** in 1992 was particularly low because of the *genocide* which occurred in that nation with inter-tribal warfare (refer ...).  

**Afghanistan** was in 1952 a monarchy and according to Wikipedia (in commenting on a purported election of the national assembly) noted that "*no census* of population has ever been undertaken" <https://en.wikipedia.org/wiki/1952_in_Afghanistan>, so it is not clear how a reliable estimate of life expectancy was made!

## Countries with life expectancy greater than 81

```{r LE>81}
gapminder %>% filter(lifeExp > 81) %>% arrange(-lifeExp)
```

## Life expectancy by continents in 2007


```{r lifexpCpnt, echo=FALSE}
boxplot(lifeExp~continent, year=2007, data=gapminder)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
